---
name: Nicholas Spyrison
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3145, Australia."
www: nspyrison.netlify.com
phone: +61 (4) 2277 0555
email: "Nicholas.Spyrison@monash.edu"
twitter: nspyrison
github: nspyrison
linkedin: nspyrison
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0044cc" # String hex color code without '#'
output: 
  vitae::hyndman:
  keep_tex: true 
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{12}{15}\sffamily}
  - \usepackage{graphicx}
  - \usepackage{amsmath}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, collapse = T)
library(tidyverse)
library(vitae)
library(unpivotr)
source("baretable.R")
```

# Education

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Text,
  2018, "\\textit{2021}", "\\textit{Ph.D. Informaiton Technology} 
    \\hfill Monash University, Clayton, VIC, AUS",
  NA, NA, "Thesis: New Tools for User-guided Exploration of Linear Projections \\hspace{60 mm}", #hspace longest line
  
  2008, 2012, "\\textit{B.Sc. Statistics}
    \\hfill Iowa State University, Ames, IA, USA",
  NA, NA, "Minors: physics and mathematics"
) 
#x <- arrange(x, -Start)
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Text) %>%
  baretable()
```


# Employment

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Position,
  2020, 2020, "Teaching assistant, data exploration and visualisation -- Monash University", # FIT 5147
  2018, 2018, "Research officer, Human geology -- Monash University", # R Language, ETL of AUS census, 3 census of Melb, 2 of Sydn 
  2019, 2019, "Teaching assistant, business and economic statistics -- Monash University", #ETC1000 
  2018, 2019, "Research officer, Criminology -- Monash University", # R Language, ETL and analysis gauguing communitiy interaction across intervention

  2016, 2018, "\\textbf{Business Intelligence Developer} --  CPI Card Group Inc.",
  NA, NA, "\\textit{T-SQL - 2012 (SSMS, SSRS), R language, GitHub, Crystal Reports, Oracle BICS, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Supply chain reporting leading to more than \\$4 M USD cost reduction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- mid-high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 4 reporting tools across multiple db instances",
  
  2015, 2016, "\\textbf{Business Intelligence Developer} -- United Dominion Realty Trust Inc. (UDR)",
  NA, NA, "\\textit{T-SQL - 2012 \\& 2016 (SSMS, SSRS, SSAS - MOLAP Cube), PowerBI, WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 3 reporting tools across several db instances",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ On-call for enterprize-wide ETL process",
  
  2014, 2015, "\\textbf{Business Intelligence Analyst} -- Heartland Financial USA Inc.",
  NA, NA, "\\textit{WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",
  
  2014, 2014, "\\textbf{Laboratory Technician} -- The Ames Laboratory & Iowa State University", # ; the Department of Physics & Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, Excel}", 
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",
  
  2013, 2014, "\\textbf{Delivery Analyst} -- International Business Machines Cooporation (IBM)",
  NA, NA, "\\textit{Excel, VBA, R language}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and mid managment",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ IBM’s process improvement methodology, root cause analysis, process behavior analysis", # IBM ver is Global distribution framework, GDF
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and mid managment",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ ETL scripting in VBA for greater than 1 FTE savings across the team",

  
  2012, 2012, "\\textbf{User Interface Developer} -- Iowa State University", # ; the Department of Statistics
  NA, NA, "\\textit{R language, GitHub, Linux Shell}",
  
  2010, 2012, "\\textbf{Laboratory Technician} -- The Ames Laboratory & Iowa State University", # ; the Department of Physics & Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, LaTeX, Excel}", 
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",
  
  2009, 2009, "\\textbf{Physics Tutor} -- Iowa State University", # ; the Department of Physics & Astronomy
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Classical physics I & II with calculus",
  
  NA, NA, NA
)
  #arrange(-Start) %>%
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Position) %>%
  baretable()
```

# Honors and awards

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2018, "ACEMS Impact and Engagement Award", # For publication of package; 'spinifex'
  2018, "UseR 2018! Datathon, third place",  # Avian temporal-spacial shiny
  2012, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL",
  2009, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL",
  2008, "American Legion award"
) %>%
  baretable()
```


# Research experience

```{r research1, results='asis'}
## TODO: UPDATE
tribble(
  ~Start, ~End, ~Project,
  2018.07, 2019.01, "\\textbf{Research Assistant}, National Natural Science Foundation of China",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Assisted in the Efficient Bayesian Flexible Density Methods with High Dimensional Financial Data Project.
  * Completed the stochastic gradient descent application to the multivariate response surface.
  * Completed the paper titled *Volatility Analysis for Housing Prices with Bayesian Response
Surface Optimization*.

```{r research2, results='asis'}
## TODO: UPDATE
tribble(
  ~Start, ~End, ~Project,
  2013.04, 2014.04, "\\textbf{Project Leader}, National Undergraduate Innovation and Entrepreneurship Training Program",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Initiated a municipal project, took charge of making overall arrangements for the project, from research topic design, official application of the project fund, plan of the theoretical approaches and research methods to the empirical analysis of the data collected from questionnaire.
  * Won the Excellent Prize upon the accomplishment of the research project.
  * Completed the paper titled *Feasibility Analysis for Developing Commercial Insurance for
Losing Only-child Problem of Single-child Families*.


# Extracurricular activities

```{r activity1, results='asis'}
## TODO: UPDATE
tribble(
  ~Start, ~End, ~Project,
  2012., 2014, "\\textbf{President}, Survey and Data Analysis Association of CUFE",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Planned a series of publicity activities for the association with more than 10 local universities warmly responding; repeatedly awarded Excellent Prize in student association activities and Advanced Individual Prize in CUFE.
  * Organized a large quantity of surveys, such as campus bus timetable investigation, campus safety improvement, research on the tutor system in CUFE; obtained several prizes in the relevant contests at different levels.
  * Twice awarded the Top Association Prize as Class A in CUFE.

```{r activity2, results='asis'}
## TODO: UPDATE
tribble(
  ~Start, ~End, ~Project,
  2013, 2014, "\\textbf{Anchor and Host}, CUFE Radio Station",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Participated in the broadcast work for the music, travel and interview group, including the script writing, recording, editing and broadcasting.
  * Host several shows and competitions in CUFE.
  * Took charge of the preparation and organization of the 5th Anniversary Celebration Evening
for thE Campus Radio Station.


