---
name: Nicholas Spyrison
address: "Department of Human-Centred Computing \\tabularnewline H600 Monash University Caulfield, VIC 3145, Australia"
www: nspyrison.netlify.com
phone: +61 (4) 2277 0555
email: "Nicholas.Spyrison@monash.edu"
twitter: nspyrison
github: nspyrison
linkedin: nspyrison
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0044cc" ## String of hex color code without '#'
output: 
  vitae::hyndman:
  keep_tex: true 
bibliography: nssPubs.bib
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{12}{15}\sffamily}
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{bibentry} #% needed for \bibentry to force print all bib entries
  - \usepackage{color} #% needed for \textcolor
  - \newcommand{\nsKeyword}{\tiny \textcolor{white}} ## Call with $\nsKeyword{text}$
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, collapse = T)
library(tidyverse)
library(vitae)
library(unpivotr)
source("baretable.R")
### Troubles with bib files:
library(RefManageR) ## printing bib entry workaround.

df <- bib2df::bib2df("./nssPubs.bib")
df
```

# Education

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Text,
  2018, "\\textit{2021}", "\\textit{(expected) Ph.D. Information Technology}
    \\hfill Monash University, Clayton, VIC, AUS",
  NA, NA, "Thesis: New Tools for User-guided Exploration of Linear Projections \\hspace{60 mm}", #hspace longest line

  2008, "2012", "\\textit{B.Sc. statistics}
    \\hfill Iowa State University, Ames, IA, USA",
  NA, NA, "Minors: physics and mathematics"
)
#x <- arrange(x, -Start)
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Text) %>%
  baretable()
```



# Employment

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Position,
  2020, 2020, "Teaching assistant, data exploration and visualization -- Monash University", # FIT 5147
  2018, 2018, "Research officer, human geology -- Monash University", # R Language, ETL of AUS census, 3 censuses of Melb, 2 of Sydn
  2019, 2019, "Teaching assistant, business and economic statistics -- Monash University", #ETC1000
  2018, 2019, "Research officer, criminology -- Monash University", # R Language, ETL and analysis gauguing communitiy interaction across intervention

  2016, 2018, "\\textbf{Business intelligence developer} --  CPI Card Group Inc.",
  NA, NA, "\\textit{T-SQL - 2012 (SSMS, SSRS), R language, GitHub, Crystal Reports, Oracle BICS, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Supply chain reporting leading to more than 4 million USD cost reduction for one location",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- mid-high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 4 reporting tools across multiple database instances",

  2015, 2016, "\\textbf{Business intelligence developer} -- United Dominion Realty Trust Inc. (UDR)",
  NA, NA, "\\textit{T-SQL - 2012 \\& 2016 (SSMS, SSRS, SSAS - MOLAP Cube), PowerBI, WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 3 reporting tools across several database instances",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ On-call for enterprize-wide nightly data process",

  2014, 2015, "\\textbf{Business intelligence analyst} -- Heartland Financial USA Inc.",
  NA, NA, "\\textit{WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",

  2014, 2014, "\\textbf{Laboratory technician} -- The Ames Laboratory \\& Iowa State University", # ; the Department of Physics \\& Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, Excel}",
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",

  2013, 2014, "\\textbf{Delivery analyst} -- International Business Machines Corporation (IBM)",
  NA, NA, "\\textit{Excel, VBA, R language}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and middle management",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ IBM’s process improvement methodology, root cause analysis, process behavior analysis", # IBM ver is Global distribution framework, GDF
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and middle management",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Automated cleaning and metric creation in VBA for greater than 1 FTE savings across the team",


  2012, 2012, "\\textbf{User interface developer} -- Iowa State University", # ; the Department of Statistics
  NA, NA, "\\textit{R language, GitHub, Linux Shell}",

  2010, 2012, "\\textbf{Laboratory technician} -- The Ames Laboratory \\& Iowa State University", # ; the Department of Physics & Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, LaTeX, Excel}",
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",

  2009, 2009, "\\textbf{Physics tutor} -- Iowa State University", # ; the Department of Physics \\& Astronomy
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Classical physics I \\& II with calculus",

  NA, NA, NA
)
  #arrange(-Start) %>%
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Position) %>%
  baretable()
```

# Honors and awards

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2018, "ACEMS Impact and Engagement Award, for development of the R package spinifex", # For publication of package; 'spinifex'
    NA, "for development of the R package spinifex",
  2018, "UseR 2018! Datathon, 3rd place, of 5 teams",
      NA, "for a temporal-spatial shiny dashboard of avian sightings in Australia",

  # 2012, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL", ## They aren't in dropbox or email, double-checked 29/03/2020.
  # 2009, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL",
  2008, "American Legion School Award",
  NA, "for character, especially 'courage, honor, service, leadership, and scholarship', as nominated by my Mock Trial coach"
) %>%
  baretable()
```

# Research summary

## Visualization of multivariate spaces
  * Between 2018 and 2021 (expected) researched linear projection visualization, especially as animations across local changes to the basis known as visualization `tours`
  * 1 accepted publication, 1 R package publication
  * Another 3 publications in the pipeline

## Superconductors, condensed matter physics
  * Between 2009 and 2014 researched pnictide superconductors (iron-based, type II superconductivity)
  * 6 publications across various compositions and dopings
  * Drafting and fabrication of fabricated tunnel-diode resonators with 0.01ppm sensitivity for contactless resistivity measurements
  * Cryogenic application up to and including vacuum turbo-pumped, He3 systems

# Membership

  * Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)
  * Statistical Society of Australia (SSA), Victorian branch
  * American Statistical Association, district 4
  * Melbourne Users of R Network (MelbURN)
  * Denver R User Group
  * Server SQL Server User Group
  * R-Ladies Melbourne
  * Not so standard deviations (R podcast)
  * The R-podcast
  * Credidibly Curious(R podcast)

# Publications

## Visualization of multivariate spaces
```{r ref-highDimVis, results='asis'}
# RefManageR::ReadBib("./nssPubs.bib")
bibliography_entries("./nssPubs.bib") %>%
  arrange(date, surnames)
```

## Superconductors, condensed matter physics
```{r ref-physics, results='asis', eval=F}
RefManageR::ReadBib("./nssPubs_physics.bib")
```


<!-- --- -->
<!-- nocite: '@*' -->
<!-- ... -->
