---
name: Nicholas Spyrison
address: "Department of Econometrics \\& Business Statistics,\\tabularnewline Monash University, VIC 3145, Australia."
www: nspyrison.netlify.com
phone: +61 (4) 2277 0555
email: "Nicholas.Spyrison@monash.edu"
twitter: nspyrison
github: nspyrison
linkedin: nspyrison
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "0044cc" ## String hex color code without '#'
output: 
  vitae::hyndman:
  keep_tex: true 
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{12}{15}\sffamily}
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  ## - \def\textkeyword{\tiny \textcolor{green}} ## Call with \\textkeyword{text}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, collapse = T)
library(tidyverse)
library(vitae)
library(unpivotr)
source("baretable.R")

#### Rob's Structure:
## Education and qualifications
## Employment history
## Other positions
## Honours and awards
## Current membership
## Research [summary]
## Grants
## Major invited talks
## Teaching
## Consulting
## Adivsory boards
## Publications (10 subsections)


#### Following this, my structure would look like: (add philosophy or no?)
## Philosophy (ADD?)
## Education
## Employment
## Honours and awards
## Research [summary: Physics, Statistics]
## Membership -- community learning and growth
## Publications
## >PhD Thesis
## >Research papers
## >Software (R packages)
## >Presentations (REMOVE?)
```

# Education

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Text,
  2018, "\\textit{2021}", "\\textit{Ph.D. Informaiton Technology} 
    \\hfill Monash University, Clayton, VIC, AUS",
  NA, NA, "Thesis: New Tools for User-guided Exploration of Linear Projections \\hspace{60 mm}", #hspace longest line
  
  2008, 2012, "\\textit{B.Sc. Statistics}
    \\hfill Iowa State University, Ames, IA, USA",
  NA, NA, "Minors: physics and mathematics"
) 
#x <- arrange(x, -Start)
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Text) %>%
  baretable()
```

<!-- $\textkeyword{TEST}$ -->

# Employment

```{r results='asis'}
x <- tribble(
  ~Start, ~End, ~Position,
  2020, 2020, "Teaching assistant, data exploration and visualisation -- Monash University", # FIT 5147
  2018, 2018, "Research officer, Human geology -- Monash University", # R Language, ETL of AUS census, 3 census of Melb, 2 of Sydn 
  2019, 2019, "Teaching assistant, business and economic statistics -- Monash University", #ETC1000 
  2018, 2019, "Research officer, Criminology -- Monash University", # R Language, ETL and analysis gauguing communitiy interaction across intervention

  2016, 2018, "\\textbf{Business Intelligence Developer} --  CPI Card Group Inc.",
  NA, NA, "\\textit{T-SQL - 2012 (SSMS, SSRS), R language, GitHub, Crystal Reports, Oracle BICS, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Supply chain reporting leading to more than \\$4 M USD cost reduction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- mid-high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 4 reporting tools across multiple db instances",
  
  2015, 2016, "\\textbf{Business Intelligence Developer} -- United Dominion Realty Trust Inc. (UDR)",
  NA, NA, "\\textit{T-SQL - 2012 \\& 2016 (SSMS, SSRS, SSAS - MOLAP Cube), PowerBI, WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ 3 reporting tools across several db instances",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ On-call for enterprize-wide ETL process",
  
  2014, 2015, "\\textbf{Business Intelligence Analyst} -- Heartland Financial USA Inc.",
  NA, NA, "\\textit{WebFOCUS – 8.0+, Excel}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ T-SQL development -- high level abstraction",
  
  2014, 2014, "\\textbf{Laboratory Technician} -- The Ames Laboratory \\& Iowa State University", # ; the Department of Physics \\& Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, Excel}", 
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",
  
  2013, 2014, "\\textbf{Delivery Analyst} -- International Business Machines Cooporation (IBM)",
  NA, NA, "\\textit{Excel, VBA, R language}",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and mid managment",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ IBM’s process improvement methodology, root cause analysis, process behavior analysis", # IBM ver is Global distribution framework, GDF
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Weekly metric/KPI presentations to lower and mid managment",
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ ETL scripting in VBA for greater than 1 FTE savings across the team",

  
  2012, 2012, "\\textbf{User Interface Developer} -- Iowa State University", # ; the Department of Statistics
  NA, NA, "\\textit{R language, GitHub, Linux Shell}",
  
  2010, 2012, "\\textbf{Laboratory Technician} -- The Ames Laboratory \\& Iowa State University", # ; the Department of Physics & Astronomy
  NA, NA, "\\textit{CAD Inventor, LabVIEW, LaTeX, Excel}", 
  # NA, NA, "\\hspace{5 mm} $\\bullet~~$ Superconductor research and aperatus fabrication",
  
  2009, 2009, "\\textbf{Physics Tutor} -- Iowa State University", # ; the Department of Physics \\& Astronomy
  NA, NA, "\\hspace{5 mm} $\\bullet~~$ Classical physics I \\& II with calculus",
  
  NA, NA, NA
)
  #arrange(-Start) %>%
x$End = replace_na(x$End, "")
x$Years = if_else(is.na(x$Start), "", paste0(x$Start, "--", x$End))
select(x, Years, Position) %>%
  baretable()
```

# Honors and awards

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2018, "ACEMS Impact and Engagement Award", # For publication of package; 'spinifex'
  2018, "UseR 2018! Datathon, third place",  # Avian temporal-spacial shiny
  2012, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL",
  2009, "LOOK UP ISU AWARDS AND HONORS HERE -- SEVERAL",
  2008, "American Legion award"
) %>%
  baretable()
```

# Research

  * High dimensional visualization via linear projections
      * Between 2018 and 2021 (expected) I researched high dimensional visualization espically trough animates across changing bases with various vizualization tours
      * One Accepted publication, one R package publication
      * Another 3 publications in the pipeline
  * Consensed mater physcis (CMP),  
      * Between 2009 and 2014 I researched pnictide superconductors (iron-based, type II superconductors)
      * 6 publications across various composistions and dopings
      * Drafting and fabrication of fabricated tunnel-diode resonators with 0.01ppm sensitivity for contactly resistivity mesurments
      * Cryogenic application up to and including including vacuum turbo-pumped, He3 systems

  
# Membership

  * Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)
  * Statistical Society of Australia (SSA), Victorian branch
  * American Statistical Association, district 4
  * Melbourne Users of R Network (MelbURN)
  * Denver R User Group
  * Senver SQL Server User Group
  * R-Ladies Melbourne
  * Not so standard diviations (R podcast)
  * The R-podcast
  * Credidibly Curious(R podcast)

# Publications

<!-- \renewcommand{\bibfont}{\normalfont\fontsize{10}{11.8}\sffamily} -->

## PhD thesis
```{r thesis, eval=F}
bibliography_entries("nssPubs.bib") %>%
  filter(bibtype == "PhdThesis") %>%
  arrange(desc(date), title)
```

## Research papers
```{r papers, eval=T}
bibliography_entries("nssPubs.bib") %>%
  filter(bibtype == "Article") %>%
  arrange(desc(date), title)
```

## Software (R packages)
```{r software, eval=F}
bibliography_entries("nssPubs.bib") %>%
  filter(bibtype == "Software") %>%
  arrange(desc(date), title)
```

## Presentations
```{r presentations, eval=F}
bibliography_entries("nssPubs.bib") %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(date), title)
```

## Research papers, physics
```{r papers-phys, eval=F}
bibliography_entries("nssPubs_physics.bib") %>%
  filter(bibtype == "Article") %>%
  arrange(desc(date), title)
```

## Presentations, physics
```{r presentations-phys, eval=F}
bibliography_entries("nssPubs_physics.bib") %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(date), title)
```

